EV Exploratory Data Analysis

### 2024-07-13 code/eda-code/eda-ev.qmd
comment out unfinished Python code block so QMD file renders correctly

```{python}
us_zips_df = read_csv(base_dir + 'data/raw-data/uszips.csv')
wa_zips = us_zips_df.loc[us_zips_df['state_id'] == 'WA']
wa_zips = wa_zips[['ZIPCODE', 'lat', 'lng', 'population']]
merge_zips = merge(wa_zips, zip_code_count, on='ZIPCODE')
# print(merge_zips)
test = base_dir + 'data/raw-data/counties.geojson'
with open(test) as f:
    gj = geojson.load(f)
    # print(gj['features'])
# countries = ["53"]
# new_list = []
# features = gj['features'][0]['properties']['STATEFP']
features = gj['features']
print(features[0])
# for i in features:
#     # print(i)
#     if i['properties']['STATEFP'] == '53':
#         new_list.append(i)
#     else:
#         pass
# final = json.dumps(new_list, indent=2)
# print(gj)
mapit = folium.Map(location=[122.511983, 37.77113])

for i in features:
    if i['properties']['STATEFP'] == '53':
        print(i)
        folium.Choropleth(geo_data=i['geometry']['coordinates'][0][0],
            data=merge_zips,
            columns=['lat', 'lng', 'Vehicle Count'],
            key_on='geometry.coordinates',
            fill_color='magma',
            line_color='magma'
        ).add_to(mapit)
# mapit.save('test.html')
# coordinates = []
# for zip_code in zip_code_count['ZIPCODE']:
#     print(zip_code)
#     geocode_result = geopandas.
    # geocode_result = gmaps.geocode(zip_code)
    # lat = geocode_result[0][‘geometry’][‘location’][‘lat’]
    # lng = geocode_result[0][‘geometry’][‘location’][‘lng’]
    # coordinates.append((lat, lng))
```

>>>>

### TO DO
```{python}
# us_zips_df = read_csv(base_dir + 'data/raw-data/uszips.csv')
# wa_zips = us_zips_df.loc[us_zips_df['state_id'] == 'WA']
# wa_zips = wa_zips[['ZIPCODE', 'lat', 'lng', 'population']]
# merge_zips = merge(wa_zips, zip_code_count, on='ZIPCODE')
# # print(merge_zips)
# test = base_dir + 'data/raw-data/counties.geojson'
# with open(test) as f:
#     gj = geojson.load(f)
    # print(gj['features'])
# countries = ["53"]
# new_list = []
# features = gj['features'][0]['properties']['STATEFP']
# features = gj['features']
# print(features[0])
# for i in features:
#     # print(i)
#     if i['properties']['STATEFP'] == '53':
#         new_list.append(i)
#     else:
#         pass
# final = json.dumps(new_list, indent=2)
# print(gj)
# mapit = folium.Map(location=[122.511983, 37.77113])

# for i in features:
#     if i['properties']['STATEFP'] == '53':
#         print(i)
#         folium.Choropleth(geo_data=i['geometry']['coordinates'][0][0],
#             data=merge_zips,
#             columns=['lat', 'lng', 'Vehicle Count'],
#             key_on='geometry.coordinates',
#             fill_color='magma',
#             line_color='magma'
#         ).add_to(mapit)
# mapit.save('test.html')
# coordinates = []
# for zip_code in zip_code_count['ZIPCODE']:
#     print(zip_code)
#     geocode_result = geopandas.
    # geocode_result = gmaps.geocode(zip_code)
    # lat = geocode_result[0][‘geometry’][‘location’][‘lat’]
    # lng = geocode_result[0][‘geometry’][‘location’][‘lng’]
    # coordinates.append((lat, lng))
```
